### 2025-03-17 mycv/mylatex_cv.tex
snapshot

    \section{Education}
        \begin{twocolentry}{Mar 2001 – Feb 2008}
            \textbf{Hanyang University}, BS, Department of Materials Science and Engineering
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2008 – Feb 2010}
            \textbf{POSTECH}, MS, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2010 – Feb 2014}
            \textbf{POSTECH}, PhD, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
        \end{twocolentry}
        \vspace{0.10 cm}

    \section{Experience}
        \begin{twocolentry}{Mar 2017 – Present}
            \textbf{Assistant, associate professor}, Changwon National University, ROK
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{July 2024 – Aug 2024}
            \textbf{Short term visitor}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Feb 2022 – Feb 2024}
            \textbf{Guest Scientist (offsite)}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Dec 2016 – Feb 2017}
            \textbf{Postdoc}, POSTECH, ROK
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2016 – Nov 2016}
            \textbf{Research Scientist}, Clemson university, SC, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2014 – Feb 2016}
            \textbf{Postdoc}, NIST, MD, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Apr 2012 – Sep 2012}
            \textbf{Research Affiliate}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{June 2011 – Dec 2011}
            \textbf{Guest Researcher}, NIST, MD, USA
        \end{twocolentry}
        \vspace{0.10 cm}

@@

    \section{Skills}
        \begin{onecolentry}
            \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
            \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
            \item Languages: Korean, English
            \item Experimental Mechanics: Uniaxial tension, shear, hydraulic bulge test, biaxial tests
            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction and analysis
            \item Computer skills: Linux, Git
        \end{onecolentry}

@@

        \begin{twocolentry}{\href{https://github.com/Jeonbohye/VPSC8-dEVPSC}{github.com/Jeonbohye/VPSC8-dEVPSC}}\textbf{VPSC8 and EVPSC} (private repo)
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Combines VPSC8 and EVPSC models
                \item Numerical implementation of VPSC, $\Delta$EVPSC, and $\sigma$EVPSC constitutive model
                \item Three separate build commands for executables of VPSC8, $\Delta$EVPSC, and $\sigma$EVPSC.
            \end{highlights}
        \end{onecolentry}

        \vspace{0.4 cm}
        \begin{twocolentry}{\href{https://github.com/youngung/texture3}{github.com/youngung/texture3}}
            \textbf{In-house Python scripts for texture analysis}
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Can plot pole figures of discrete orientations used in VPSC-like crystal plasticity codes
                \item Written entirely in Python with open-sourced libraries including matplotlib, NumPy and SciPy
            \end{highlights}
        \end{onecolentry}
        \vspace{0.2 cm}
        \section{Misc.}
        \begin{twocolentry}{2023-present}
            \begin{highlights}
                \item Board member of Korean Society for Technology of Plasticity
            \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \begin{twocolentry}{2019-present}
            \begin{highlights}
                \item Editoiral board member of Korean Journal of Metals and Materials
            \end{highlights}
        \end{twocolentry}
    \vspace{0.2 cm}
    \newpage
    \section{Full list of publications}
    \begin{enumerate}
        \item
        \begin{twocolentry}{submitted}
            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        %\begin{onecolentry}
        %    {\it }
        %\end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}

>>>>

    \section{Education}
        \begin{twocolentry}{03/01/2001 – 02/29/2008}
            \textbf{Hanyang University}, BS, Department of Materials Science and Engineering
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{03/01/2008 – 02/28/2010}
            \textbf{POSTECH}, MS, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{03/01/2010 – 02/28/2014}
            \textbf{POSTECH}, PhD, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
        \end{twocolentry}
        \vspace{0.10 cm}

    \section{Experience}
        \begin{twocolentry}{03/01/2017 – Present}
            \textbf{Assistant, associate professor}, Changwon National University, ROK
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{07/11/2024 – 08/16/2024}
            \textbf{Short term visitor}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{02/01/2022 – 02/1/2024}
            \textbf{Guest Scientist (offsite)}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{12/01/2016 – 02/28/2017}
            \textbf{Postdoc}, POSTECH, ROK
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{03/01/2016 – 11/30/2016}
            \textbf{Research Scientist}, Clemson university, SC, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{03/01/2014 – 02/29/2016}
            \textbf{Postdoc}, NIST, MD, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{04/01/2012 – 09/30/2012}
            \textbf{Research Affiliate}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{06/01/2011 – 12/31/2011}
            \textbf{Guest Researcher}, NIST, MD, USA
        \end{twocolentry}
        \vspace{0.10 cm}

@@

    \section{Skills}
        \begin{onecolentry}
            \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
            \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
            \item Languages: Korean, English
            \item Experimental Mechanics: uniaxial tension, shear, hydraulic bulge test, biaxial tests, digital image correlation (DIC)
            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction (EBSD), Residual stress analysis
            \item Computer skills: Linux, Git
        \end{onecolentry}

@@

        \begin{twocolentry}{\href{https://github.com/Jeonbohye/VPSC8-dEVPSC}{github.com/Jeonbohye/VPSC8-dEVPSC}}\textbf{VPSC8 and EVPSC} (private repo)
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Combines VPSC8 and EVPSC models
                \item Numerical implementation of VPSC, $\Delta$EVPSC, and $\sigma$EVPSC constitutive model
                \item Three separate build commands for executables of VPSC8, $\Delta$EVPSC, and $\sigma$EVPSC.
            \end{highlights}
        \end{onecolentry}
        \vspace{0.4 cm}

        \begin{twocolentry}{\href{https://github.com/youngung/texture3}{github.com/youngung/texture3}}
            \textbf{In-house Python scripts for texture analysis}
        \end{twocolentry}
        \begin{onecolentry}
            \begin{highlights}
                \item Can plot contoured pole figures and inverse pole figures from discrete orientations
                \item Written entirely in Python with open-sourced libraries including matplotlib, NumPy and SciPy
                \item Can generate RGB maps of EBSD (electron basck-scattered diffraction) scans
            \end{highlights}
        \end{onecolentry}
        \vspace{0.4 cm}

        \section{Misc.}
        \begin{twocolentry}{2023-present}
          \begin{highlights}
          \item Board member of Korean Society for Technology of Plasticity
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \begin{twocolentry}{2019-present}
          \begin{highlights}
          \item Editoiral board member of Korean Journal of Metals and Materials
          \end{highlights}
        \end{twocolentry}
        \vspace{0.2 cm}
        \newpage
        \section{Full list of publications}
        \begin{enumerate}
        \item
          \begin{twocolentry}{submitted}
            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        %\begin{onecolentry}
        %    {\it }
        %\end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}
